---
title: "lab06versioncontrol"
author: "Krista Waugh"
date: "3/6/2019"
output: html_document
---


On branch master

No commits yet

Changes to be committed:
  (use "git rm --cached <file>..." to unstage)

	new file:   README.md

calvisitor-10-105-150-86:demo-repo kristawaugh$ git commit -m "first commit"

calvisitor-10-105-150-86:demo-repo kristawaugh$ git status

calvisitor-10-105-150-86:demo-repo kristawaugh$ git remote add origin https://github.com/kristawaugh/demo-repo.git
calvisitor-10-105-150-86:demo-repo kristawaugh$ git remote -v

calvisitor-10-105-150-86:demo-repo kristawaugh$ git status

calvisitor-10-105-150-86:demo-repo kristawaugh$ git push origin master

calvisitor-10-105-150-86:demo-repo kristawaugh$ git status

calvisitor-10-105-150-86:demo-repo kristawaugh$ git remote -v

calvisitor-10-105-150-86:demo-repo kristawaugh$ git push origin master

krista 

```{r eval=FALSE}
echo "# Demo Repo" >> README.md
git init
git add README.md
git commit -m "first commit"
git remote add origin https://github.com/gastonstat/demo-repo.git
git push -u origin master
```

```{r eval = FALSE}
cd desktop
mkdir demo-repo
cd demo-repo
git init
```

```{r eval = FALSE}
echo "# Demo Repo" >> README.md
git status
git add README.md 
git status 
git commit -m "first commmit"
```

```{r eval = FALSE}
git remote add origin https://github.com/username/demo-repo.git
git remote -v
```

```{r eval =FALSE}
git status 
git push origin master 
```

